Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-05 Paper/results.tex
fix last sentence
minor change to Sec. IV.B.1

For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
(potential temperature equation and subgrid-scale kinetic energy equation).
Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
step, in this work we use two Picard iterations for every time step.
Each Picard iteration requires a Poisson solve and five Helmholtz solves
(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
and manipulating unstructured data.

>>>>

For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
A time step within AMR-Wind requires two Poisson solves (MAC and nodal projection),
a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
(potential temperature equation and subgrid-scale kinetic energy equation).
Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
step, in this work we use two Picard iterations for every time step.
Each Picard iteration requires a Poisson solve and five Helmholtz solves
(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
implementation, and additional study is required to understand the performance comparisons.
The most significant difference between the two solvers is that AMR-Wind uses structured grids
whereas Nalu-Wind uses unstructured grids. The differences in performance can be attributed with the 
computational overhead of storing and manipulating unstructured data.
